Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-08-05 bbbq_article.tex
Show tables

\begin{table}[!htbp]
  \input{bbbq_1/bbbq_1_percentages.latex}
  \caption{
    Percentage of MHC-I epitopes overlapping with transmembrane helix.
    \richel{This is simulated data}
  }
  \label{table:bbbq_1_percentages}
\end{table}

\begin{table}[!htbp]
  \input{bbbq_1/bbbq_1_stats_covid.latex}
  \caption{
    Kolmogorov-Smirnov test results comparing human and COVID-19 for MHC-I
    \richel{Done on the simulated data}
  }
  \label{table:bbbq_1_stats_covid}
\end{table}

\begin{table}[!htbp]
  \input{bbbq_1/bbbq_1_stats_myco.latex}
  \caption{
    Kolmogorov-Smirnov test results comparing human and Mycobacterium for MHC-I
    \richel{Done on the simulated data}
  }
  \label{table:bbbq_1_stats_myco}
\end{table}

@@

\begin{table}[!htbp]
  \input{bbbq_2/bbbq_2_percentages.latex}
  \caption{
    Percentage of MHC-II epitopes overlapping with transmembrane helix.
    \richel{This is simulated data}
  }
  \label{table:bbbq_2_percentages}
\end{table}

\begin{table}[!htbp]
  \input{bbbq_2/bbbq_2_stats_covid.latex}
  \caption{
    Kolmogorov-Smirnov test results comparing human and COVID-19 for MHC-II
    \richel{Done on the simulated data}
  }
  \label{table:bbbq_2_stats_covid}
\end{table}

\begin{table}[!htbp]
  \input{bbbq_2/bbbq_2_stats_myco.latex}
  \caption{
    Kolmogorov-Smirnov test results comparing human and Mycobacterium for MHC-II
    \richel{Done on the simulated data}
  }
  \label{table:bbbq_2_stats_myco}
\end{table}

>>>>

\input{bbbq_1/table_tmh_binders_mhc1.latex}

%\begin{table}[!htbp]
%   \input{bbbq_1/bbbq_1_stats_covid.latex}
%   \caption{
%     Kolmogorov-Smirnov test results comparing human and COVID-19 for MHC-I
%     \richel{Done on the simulated data}
%   }
%   \label{table:bbbq_1_stats_covid}
% \end{table}

% \begin{table}[!htbp]
%   \input{bbbq_1/bbbq_1_stats_myco.latex}
%   \caption{
%     Kolmogorov-Smirnov test results comparing human and Mycobacterium for MHC-I
%     \richel{Done on the simulated data}
%   }
%   \label{table:bbbq_1_stats_myco}
% \end{table}

@@

\input{bbbq_1/table_tmh_binders_mhc2.latex}

% \begin{table}[!htbp]
%   \input{bbbq_2/bbbq_2_stats_covid.latex}
%   \caption{
%     Kolmogorov-Smirnov test results comparing human and COVID-19 for MHC-II
%     \richel{Done on the simulated data}
%   }
%   \label{table:bbbq_2_stats_covid}
% \end{table}

% \begin{table}[!htbp]
%   \input{bbbq_2/bbbq_2_stats_myco.latex}
%   \caption{
%     Kolmogorov-Smirnov test results comparing human and Mycobacterium for MHC-II
%     \richel{Done on the simulated data}
%   }
%   \label{table:bbbq_2_stats_myco}
% \end{table}
